Implementation of poloidal density variation in collision operator

### 2018-01-18 doc/manual/version3/inputParameters.tex
Added testingInnerProduct. adjointRHS construction and innerProduct now pass test.

{\ttfamily RHSMode} = 4: Solve the adjoint equation at constant $E_r$. This must be used with {\ttfamily geometryScheme == 5}, stellarator symmetric geometry, {\ttfamily includePhi1 = .false.}, {\ttfamily EParallelHat == 0}, {\ttfamily useDKESExBDrift == .false.}, {\ttfamily magneticDriftScheme == 0}, {\ttfamily includeXDotTerm == .true.}, {\ttfamily constraintScheme == 1}, and {\ttfamily collisionOperator == 0}. \\

>>>>

{\ttfamily RHSMode} = 4: Solve the adjoint equation at constant $E_r$. This must be used with {\ttfamily geometryScheme == 5}, stellarator symmetric geometry, {\ttfamily includePhi1 = .false.}, {\ttfamily EParallelHat == 0}, {\ttfamily useDKESExBDrift == .false.}, {\ttfamily magneticDriftScheme == 0}, {\ttfamily includeXDotTerm == .true.}, {\ttfamily constraintScheme == 1} of -1, {\ttfamily geometryScheme == 5}, and {\ttfamily collisionOperator == 0}. \\
